\documentclass[12pt]{article}
\usepackage{fullpage,times}

%\pagestyle{empty}

\begin{document}

{\Huge

INTRO

\begin{itemize}

\item Game we're going to show in a minute is a content game.

\item But first, let's think deeply about the content of the human world.

\item Two pieces of content, arrowhead to iPhone span between hands.

\item 4000 years of incremental development across hundreds of loosely coordinated human generations.

\item We tend to think that we didn't have iPhones 4000 years ago because we didn't know HOW to make them.

\item What if it just took 4000 years to build the necessary infrastructure?

\item Here's a thought experiment:  If we had to start over again from scratch, naked in the wilderness with no technology, but we got to keep all of our modern knowledge, how long would it take us to get back to the iPhone?

\item Would we do it in one human lifetime?  Remember, we're starting with rocks and sticks.  Certainly more than one lifetime, and is it possible that it would take thousands of years the second time around just like the first time?

\item Make a game about this process:  a group of people starting from scratch, naked in the wilderness, and trying to coordinate a large-scale civilization building project across multiple generations.

\item In real life, each playing a small part in the middle of a very long story.

\item We've got hazy tales of what happened before we were born, and no access at all to what happens after we die.

\item We each have a very short time to make our little contribution to the world, and then we're gone.  We leave the rest up to those who come after us.

\item Hopefully, what we do in our lifetime will somehow be useful to them.

\item Imagine a multiplayer server filled with untouched wilderness that stretches infinitely in all directions.

\item The first player who joins the server is Eve, she's the  first human being in this world, and she starts at the coordinates 0,0, trying to survive.

\item Eve, and everyone else who joins the server, will live approximately one hour of real time, with each minute equalling year in the game.

\item The second player to join the server is born to Eve as her first child, and this player starts out as a totally helpless baby.

\item If Eve helps them, they might survive to adulthood and be able to live on their own, but without help, they won't even survive a minute, and they'll die in infancy.

\item Later players who join the server are born to Eve's grown children.  These children and grandchildren form the family tree that will perpetuate civilization over the long haul on the server.  With each player participating for about an hour before dying.

\item Dead players can rejoin the world, but only as helpless babies born to other parents in different circumstances elsewhere in the world.  None of us can pick the situation that we're born into.


\item So, what's the scope of what we're trying to make here?

\item This is a content game about what its like to make the content of our world from scratch.

\item And we're aiming high, let's say 10,000 full interactive, craftable objects.

\item But we're not gonna spend 4000 years making this game.

\item The plan is for 2 people to do it in one year of part time work.

\item In order to do this, we need to rethink content creation.

\item We need to be able to add stuff to the game at the speed of thought.

\item We can't be drawing stuff one pixel at a time or tweaking stuff forever in PhotoShop.

\item What if we could do it with hand drawn stuff?

\item Can we get it into the game as quickly as we can doodle it on paper with no digital retouching?

\item I'm going to show you an editor that lets us do this.

\end{itemize}

\newpage 

EDITOR DEMO

\begin{itemize}

\item Show Mickey as baby.

\item Mouse over separate, hand drawn parts.

\item Procedural aging system, but first:

\item Puberty question?

\item Show aging.

\item Before, I said I wanted the objects in the game to be deeply interactive, so how are we going to make that happen without a lot of custom coding for each object?

\item Think of how Minecraft finally managed a deep simulation and physical space by breaking the landscape into very coarse, less realistic one meter blocks.

\item We could do things we'd never done in a game before, like dig a cave under the ocean and have that cave fill up with ocean water.

\item Is there an equivalent coarse representaion for object interaction?

\item I think I've discovered one.

\item What if we break every interaction down to A + B = C?

\item This is very coarse, but it seems to capture almost everything people do with objects in our world.

\item Allows for some surpringly nuanced interaction chains.

\item Example:  bowl of dough.

\item I'm going to show just how fast we can add content to the game using this editor by adding a new object to the game right now.

\item Hold up sketch of car.

\item Scan it, edit it, animate it.

\end{itemize}

}

\end{document}
